\chapter*{Presentations and publication List}
\addcontentsline{toc}{chapter}{Presentations and publication List}
%\hspace {0.75cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%{\Large{\bfseries{Presentations}}}

\section*{Presentations}

\begin{enumerate}
  
\item Jun. 2014, Characterizing eA collision geometry with forward neutrons at an EIC, oral presentation,
  \textbf{Electron-Ion Collider Users Meeting}, Upton, NY, USA
  
\item Oct. 2013, Studies of e+A physics at an EIC, oral presentation,
  \textbf{Fall meeting of the Division of Nuclear Physics of the American Physical Society}, Newport News, VA, USA
  
\item Nov. 2012, Monte Carlo Simulation Techniques Used in the Study of Different Physics Channels at the Future eRHIC Project, oral presentation,
  \textbf{BNL Young Researcher Symposium}, Upton, NY, USA  
  
\item Oct. 2012, Dihadron Correlations in the eA program at an Electron Ion Collider, oral presentation,
  \textbf{Fall meeting of the Division of Nuclear Physics of the American Physical Society}, Newport Beach, CA, USA

\item Jul. 2012, Dihadron Correlations at eRHIC and Monte Carlo Development, oral presentation,
  \textbf{Riken BNL Research Center Workshop on Forward Physics at RHIC}, Upton, NY, USA

\item Oct. 2011, Studying the nucleus via dihadron correlation with an Electron-Ion Collider, oral presentation,
  \textbf{Fall meeting of the Division of Nuclear Physics of the American Physical Society}, East Lansing, MI, USA

\item Aug. 2010, Equillibrium Thermostatistics for Finite System with Energy Nonextensivity, oral presentation,
  \textbf{The 16th National Conference on Condensed Matter Theory and Statistical Physics}, Changchun, Jilin, China
  
  
%\item Jun. 2014, Characterizing eA collision geometry with forward neutrons at an EIC, oral presentation,
%  \textbf{XXXX Meeting}, Upton, NY, USA
%  
%\item Oct. 2013, Studies of e+A physics at an EIC, oral presentation,
%  \textbf{Fall meeting of XXXX of the American Physical Society}, Newport News, VA, USA
%  
%\item Nov. 2012, Monte Carlo Simulation Techniques Used in the Study of Different Physics Channels at the Future eRHIC Project, oral presentation,
%  \textbf{XXXX Symposium}, Upton, NY, USA  
%  
%\item Oct. 2012, Dihadron Correlations in the eA program at an Electron Ion Collider, oral presentation,
%  \textbf{Fall meeting of XXXX of the American Physical Society}, Newport Beach, CA, USA
%
%\item Jul. 2012, Dihadron Correlations at eRHIC and Monte Carlo Development, oral presentation,
%  \textbf{XXXX Workshop on Forward Physics at RHIC}, Upton, NY, USA
%
%\item Oct. 2011, Studying the nucleus via dihadron correlation with an Electron-Ion Collider, oral presentation,
%  \textbf{Fall meeting of XXXX of the American Physical Society}, East Lansing, MI, USA
%
%\item Aug. 2010, Equillibrium Thermostatistics for Finite System with Energy Nonextensivity, oral presentation,
%  \textbf{The 16th National Conference on XXXX}, Changchun, Jilin, China
%  
  
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%{\Large{\bfseries{Publication list}}}

\section*{Publication list}

\begin{enumerate}

\item \textbf{L. Zheng}, E.C. Aschenauer, J.H. Lee, Determination of Electron-Nucleus Collision Geometry with Forward Neutrons,
  arXiv:1407.8055

\item \textbf{L. Zheng}, E.C. Aschenauer, J.H. Lee, Bo-wen Xiao, Probing Gluon Saturation through Dihadron Correlations at an Electron-Ion Collider ,
  Proceedings of Science (DIS2014), 255, 2014
  
\item \textbf{L. Zheng}, E.C. Aschenauer, J.H. Lee, Bo-wen Xiao, Probing Gluon Saturation through Dihadron Correlations at an Electron-Ion Collider ,
 Phys. Rev. D, \textbf{89}, 074037, 2014
 
\item \textbf{Zheng L}, Li W, Thermoequilibrium statistics for a finite system with energy nonextensivity,
Chinese Sci. Bull., \textbf{56}, 3666, 2011
  
%\item \textbf{XXX}, XXX, XXX, Determination of Electron-Nucleus Collision Geometry with Forward Neutrons,
%  arXiv:XXX
%  
%\item \textbf{XXX}, XXX, XXX, XXX, Probing Gluon Saturation through Dihadron Correlations at an Electron-Ion Collider ,
%  Proceedings of Science (DIS2014), XXX, 2014
%
%\item \textbf{XXX}, XXX, XXX, XXX, Probing Gluon Saturation through Dihadron Correlations at an Electron-Ion Collider ,
% Phys. Rev. D, \textbf{XX}, XXXX, 2014
%
%\item \textbf{XXX}, XXX, Thermoequilibrium statistics for a finite system with energy nonextensivity,
%Chinese Sci. Bull., \textbf{XX}, XXX, 2011

\end{enumerate}


\section*{EIC Publications}
\begin{enumerate}
\item A. Accardi et al., Electron Ion Collider: The Next QCD Frontier - Understanding the glue that binds us all,
 arXiv:1212.1701
 
\item E.C. Aschenauer et al., eRHIC Design Study: An Electron-Ion Collider at BNL, arXiv:1409.1633
%
%\item XXX et al., Electron Ion Collider: The Next QCD Frontier - Understanding the glue that binds us all,
% arXiv:XXX
% 
%\item XXX et al., eRHIC Design Study: An Electron-Ion Collider at BNL, arXiv:XXX

\end{enumerate}


